### 2018-07-21 paper/design.tex
Points out that Sohinxes is a bounded random walk

We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
Sphinxes provides, just as Sphinx, source-routed (communication model), 
unidirectional (network structure), message-based (performance) communication.
As such, it relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set).

>>>>

We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
Sphinxes provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, Sphinxes is hybrid source-hop-by-hop routed (communication 
model),
Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set).

### 2018-07-21 paper/security-discussion.tex
Points out that Sohinxes is a bounded random walk

>>>>

\sonja{will add some framing about us composing and modifying parts that
  have security proofs for their original and individual versions and needing to evaluate the resulting schemes}

\commentDaniel{Predecessor attacks: random walk protocols has the problem that 
  the adversary can see the initiator (statistically) more often than the other 
  nodes, and can thus identify the 
  source~\cite{RoutingSurveyAnonymousProtocols}.
  Our protocol is a \enquote{bounded} random walk, \ie within limits.}
